### 2019-12-17 tex/ms.tex
more text and editing

In order to validate the system throughput as measured by the DESI GFA cameras, we must first perform an analysis to determine the expected throughput and photometric zeropoint. The primary goal of this analysis is to predict the $r$ band AB magnitude of a source that would correspond to a total detected DESI GFA signal of 1 electron per second. The factors that contribute to determining the DESI GFA throughput are: the atmosphere, the Mayall telescope primary mirror reflectivity, the corrector throughput (including vignetting at the radius of the GFA cameras), the GFA $r$ band filter transmission profile and the GFA detector quantum efficiency (QE). These individual factors are overplotted together in Figure \ref{fig:throughput_factors}.

@@

The atmospheric transmission is taken from a file called \verb|ZenithExtinction-KPNO.fits|, found in the desimodel product\footnote{\url{https://desi.lbl.gov/svn/code/desimodel/trunk/data/inputs/throughput/ZenithExtinction-KPNO.fits}}. The Mayall telescope primary mirror reflectivity and corrector throughput were taken from ``DESI-347-v14 Throughput Noise SNR Calcs''. The GFA filter transmission was extracted from ``DESI-1297 GFA Filter verification data''. The GFA CCD QE was extracted from the e2v data sheet ``CCD230-42 Back Illuminated Scientific CCD Sensor'', specifically the plot on page 4. Note that the DESI GFA detectors have the `Basic midband coating' option (i.e., the green line in the data sheet's QE plot). The resulting total throughput is shown in Figure \ref{fig:total_throughput}.

@@

In order to use the total throughput curve to calculate a predicted zeropoint in AB magnitudes, we additionally need to take into account the mirror area. We adopt a value of 8.66 square meters for the Mayall primary mirror area based on DESI-347-v15. Combining the throughput curve, the definition of the AB magnitude system, and the Mayall primary mirror area we calculate a predicted GFA zeropoint of $r$ = 27.00 AB for a source with total detected signal of 1 electron per second (assuming airmass = 1). This computation is run using the following command:

@@

% mention "dense fields" program name

% check the 22 value above...

% justification for why this is a good data set to use
%     very close to airmass = 1
%     the unique exposure times in this data set are 30-60 seconds

% make clear that the analysis described here only pertains to the six in-focus guide cameras, and ignores the four out-of-focus cameras
% perhaps in the future i can update the analysis to include checking the zeropoints of the focus cameras as well

@@

Table \ref{tab:zps} lists the zeropoint values obtained in terms of both ADU/s and e-/s on a per-amp basis for all six guide GFA cameras. The zeropoints in terms of ADU are applicable to the raw data --- they do not have any flat fielding baked in. In all cases the zeropoints correspond to total light, night signal within some nominal aperture.

@@

A key assumption underlying our comparison of the measured GFA zeropoints to our zeropoint prediction is that we are using the correct GFA exposure time in computing the signal as a rate in detected electrons per second. GFA exposure times in seconds are accessed via the EXPTIME header keyword. Given the discussion about GFA timestamp oddities (e.g., [desi-commiss 2976]) and the unshuttered cameras, I decided to check how well the integration time agrees with the reported EXPTIME. It's also particularly interesting to double check EXPTIME because there are relatively few ways that the measured GFA zeropoint could be slightly \textit{deeper} than the prediction (as we have found, by 6\%), but one such possibility is that the true GFA integration time is longer than what we are assuming based on the reported GFA EXPTIME values.

@@

% say what the vertical yellow line means...

>>>>

In order to validate the system throughput as measured by the DESI GFA cameras, we must first perform an analysis to determine the expected throughput and photometric zeropoint. The primary goal of this analysis is to predict the $r$ band AB magnitude of a source that would correspond to a total detected DESI GFA signal of 1 electron per second. The factors that contribute to determining the DESI GFA throughput are: the atmosphere, the Mayall telescope primary mirror reflectivity, the corrector throughput (including vignetting at the radius of the GFA cameras), the GFA $r$ band filter transmission profile and the GFA detector quantum efficiency (QE). For the radius of the GFA cameras, we use 1.574$^{\circ}$, based on template WCS solutions trained on Gaia star locations in real GFA images. These individual factors are overplotted together in Figure \ref{fig:throughput_factors}.

@@

The atmospheric transmission is taken from a file called \verb|ZenithExtinction-KPNO.fits|, found in the desimodel product\footnote{\url{https://desi.lbl.gov/svn/code/desimodel/trunk/data/inputs/throughput/ZenithExtinction-KPNO.fits}}. The Mayall telescope primary mirror reflectivity and corrector throughput and vignetting were taken from ``DESI-347-v14 Throughput Noise SNR Calcs''. The GFA filter transmission was extracted from ``DESI-1297 GFA Filter verification data''. The GFA CCD QE was extracted from the e2v data sheet ``CCD230-42 Back Illuminated Scientific CCD Sensor'', specifically the plot on page 4. Note that the DESI GFA detectors have the `Basic midband coating' option (i.e., the green line in the data sheet's QE plot). The resulting total throughput is shown in Figure \ref{fig:total_throughput}.

@@

In order to use the total throughput curve to calculate a predicted zeropoint in AB magnitudes, we additionally need to take into account the mirror area. We adopt a value of 8.66 square meters for the Mayall primary mirror area based on DESI-347-v15. Combining the throughput curve, the definition of the AB magnitude system, and the Mayall primary mirror area we calculate a predicted GFA zeropoint of $r$ = 27.026 AB for a source with total detected signal of 1 electron per second (assuming airmass = 1). This computation is run using the following command:

@@

% perhaps in the future i can update the analysis to include checking the zeropoints of the focus cameras as well

@@

Table \ref{tab:zps} lists the zeropoint values obtained in terms of both ADU/s and e-/s on a per-amp basis for all six guide GFA cameras. The zeropoints in terms of ADU are applicable to the raw data --- they do not have any flat fielding baked in. In all cases the zeropoints correspond to total light, night signal within some nominal aperture. The median zeropoint in terms of e-/second is $r$ = 27.062 AB. This is slightly (3.4\%) deeper than the predicted zeropoint of $r$ = 27.026 AB for a source with total detected signal of 1 e-/second.

@@

A key assumption underlying our comparison of the measured GFA zeropoints to our zeropoint prediction is that we are using the correct GFA exposure time in computing the signal as a rate in detected electrons per second. GFA exposure times in seconds are accessed via the EXPTIME header keyword. Given the discussion about GFA timestamp oddities (e.g., [desi-commiss 2976]) and the unshuttered cameras, I decided to check how well the integration time agrees with the reported EXPTIME. It's also particularly interesting to double check EXPTIME because there are relatively few ways that the measured GFA zeropoint could be slightly \textit{deeper} than the prediction (as we have found, by $\sim$3-4\%), but one such possibility is that the true GFA integration time is longer than what we are assuming based on the reported GFA EXPTIME values.

@@

% say what the vertical yellow line means...
% say what the red line means, emphasize that its slope is fixed to be exactly 1, not fit to match the data
